---
title: "CTX_M regularization"
author: "Rob Arbon"
date: "20/08/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This document will fit a model using Bayesian regularisation.

```{r}
library(tidyverse)
```

Load dataframe (available at request via NERC open access)

Perform the following cleaning:
o	Removal of zero plain counts
o	Scale and centre numerical variables
o	Selected only relevant antibiotic usage variables
o	Remove variables with too few or too many levels
o	Make the dependent variable an integer

# Bayesian lasso

```{r}
# Label variables into categories 
main_vars <- c('total_mg_pcu', 'ceph_3_4', 'ceph_1')
re <- 'farm'
dv <- 'ctx_m'
all_named_vars <- c(dv, re, main_vars)

# sort variables for ease
df <- dplyr::select(df, all_named_vars, dplyr::everything())


# Make a formula
names_classes <- sapply(names(df), function(x) class(df[[x]]))
```

Reference used for the following:

Carvalho CM, Polson NG, Scott JG, The horseshoe estimator for sparse signals, Biometrika, 2010; 97:465-480


```{r}
# Make formula for horseshoe variables
horse_form <- ""
for (i in 1:length(names_classes)){
  x <- names(names_classes)[i]
  # don't add random effects, dependent variables or the main testing variables. 
  if (!x %in% c(re, dv, main_vars)){
    if ('ordered' %in% names_classes[x][[1]]){
      
      horse_form <- paste(horse_form, sprintf('%s', x), sep='+')
    }else{
      horse_form <- paste(horse_form, sprintf('%s', x), sep='+')
    }    
  }
}
horse_form <- substring(horse_form, 2)
```

## Fit model

```{r}
library(brms)

# This follows the example https://discourse.mc-stan.org/t/horseshoe-prior-on-subset-of-predictors/8140/4
# Write a maximally explicit formula: dependent_var ~ main_vars + regularized_vars + random effect

form <- bf(ctx_m ~  main + reg + rand, nl=T)
form <- form + lf(rand ~ 0 + (1|farm), cmc=F, center=F)
form <- form + lf("main ~ total_mg_pcu+ceph_3_4+ceph_1",cmc=F)
form <- form + lf(paste("reg ~ 0 + ",horse_form), cmc=F)

# check which priors we need
get_prior(form, data=df, family=bernoulli)

# define the priors 
priors <- c(prior(student_t(3, 0, 10), class="b", nlpar="main", coef='Intercept'),
            prior(normal(0, 5), class="b", nlpar="main"),
            prior(horseshoe(1), class="b", nlpar="reg"))

# Run model
bmod <- brm(formula = form,
            data=df,
            family=bernoulli,
            prior=priors,
            warmup = 1000, iter = 2000, chains = 4, seed=42, cores=4, control = list(adapt_delta = 0.98))
```

```{r}
mod <- bmod

fix_df <- data.frame(fixef(mod))
fix_df$term <- row.names(fix_df)

fix_df <- fix_df %>%
  dplyr::select(term, everything()) %>%
  arrange(desc(abs(Estimate))) %>%
  filter(!grepl('Intercept', term)) %>%
  mutate(term=gsub('reg_|main_', '', term))%>%
  mutate_at(vars(-term), exp)
head(fix_df, 20)

```

