---
title: "Amox measurement error"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(brms)
library(bayestestR)

```

# Introduction

This document will fit the Bayesian amoxicillin model.

Load dataframe (available at request via NERC open access)

Perform the following cleaning:
o	Removal of zero plain counts
o	Scale and centre numerical variables EXCEPT plain_undiluted
o	Selected only relevant antibiotic usage variables
o	Remove variables with too few or too many levels
o	Make the dependent variable an integer

# Sensitivity

This is the formula we will use to determine sensitivity

k= plain count
q= min prevalence we wish to detect

$$
s = 1-(1-q)^k
$$

## Create sensitivity and specificity columns

```{r}

#specify min prevalence
q=0.01 #  ie min prevalence of 1%

df <- mutate(df, fnr=(1-q)^plain_undiluted, 
                sens = 1-fnr,
             spec=1)%>%
  dplyr::select(-fnr)


```



# Bayesian lasso

```{r}

# Label variables into different categories and sort within df
main_vars <- c('total_mg_pcu', 'tet', 'fq', 'amox', 'cefalexin', 'strep', 'ceph_1', 'co_amox', 'pen', 's_temp')
re <- 'farm'
dv <- 'amoxR'
all_named_vars <- c(dv, re, main_vars)

df <- dplyr::select(df, all_named_vars, dplyr::everything())

# Make a formula
names_classes <- sapply(names(df), function(x) class(df[[x]]))
```

Reference used for the following:

Carvalho CM, Polson NG, Scott JG, The horseshoe estimator for sparse signals, Biometrika, 2010; 97:465-480

```{r}
# Make formula for regularised variables
horse_form <- ""
for (i in 1:length(names_classes)){
  x <- names(names_classes)[i]
  # don't add random effects, dependent variables, the main testing variables or plain count. 
  if (!x %in% c(re, dv, main_vars, "plain_undiluted", "sens", "spec")){
    if ('ordered' %in% names_classes[x][[1]]){
      
      horse_form <- paste(horse_form, sprintf('%s', x), sep='+')
    }else{
      horse_form <- paste(horse_form, sprintf('%s', x), sep='+')
    }    
  }
}
horse_form <- substring(horse_form, 2)
```

## Fit model
### Temp included as measurement error using me function and scaled standard deviation of monthly average temperatures

https://discourse.mc-stan.org/t/horseshoe-prior-on-subset-of-predictors/8140/4

```{r}

# Write out the full formula

form <- bf(amoxR ~ (sens + spec - 1)/(1+exp(-eta)) + (1-spec),
          nl=TRUE)
form <- form + nlf(eta ~ main + reg + rand)
form <- form + lf(main ~ total_mg_pcu+ tet+ fq+ amox+ cefalexin+ strep+ ceph_1+ co_amox+ pen+ me(s_temp, 0.61), cmc=F) 
form <- form + lf(rand ~ 0 + (1|farm), cmc=F, center = F)
form <- form + lf(paste("reg ~ 0 + ",horse_form), cmc=F)

# find out which priors we need

get_prior(form, data=df, family=bernoulli(link="identity"))

# define the priors

priors <- c(prior(student_t(3, 0, 10), class="b", nlpar="main", coef='Intercept'),
            prior(normal(0, 5), class="b", nlpar="main"),
            prior(horseshoe(1), class="b", nlpar="reg"))


#Run model
bmod2 <- brm(formula = form,
            data=df,
            family=bernoulli(link="identity"),
            prior=priors,
            warmup = 1000, iter = 10000, thin=2, chains = 4, seed=42, cores=4, control = list(adapt_delta = 0.98))
summary(bmod2)

```




```{r}
# create model output df
mod_df <- function(mod){
  fix_df <- data.frame(fixef(mod))
  fix_df$term <- row.names(fix_df)

  tmp <- effective_sample(mod)%>%
    mutate(Parameter=str_remove(Parameter, "b_"))%>%
    dplyr::rename(term=Parameter, Eff.sample_size=ESS)%>%
    filter(!term=="main_intercept")

  fix_df <- left_join(fix_df, tmp, by=c("term"))
  fix_df <- fix_df %>%
    dplyr::select(term, everything(), -Est.Error) %>%
    #arrange(desc(abs(Estimate))) %>%
    filter(!grepl('Intercept', term)) %>%
    mutate_at(vars(-term, -Eff.sample_size), exp) %>%
    dplyr::rename(Variable=term, OR=Estimate, Lwr_CI=Q2.5, Upr_CI=Q97.5) %>%
    mutate(sig=if_else((Lwr_CI>1&Upr_CI>1)|(Lwr_CI<1&Upr_CI<1), 1, 0))
  sig <- filter(fix_df, sig==1)%>%
    dplyr::select(-sig)
  print(fix_df)
  print(sig)
}
mod_df(bmod2)

```

# Skeptical priors

Rerun with skeptical priors on the main variables
- we don't expect antibiotics or temp to be protective so set this as the mean for the main vars


```{r}

# define the priors 

priors <- c(prior(student_t(3, 0, 10), class="b", nlpar="main", coef='Intercept'),
            prior(normal(-0.5, 2), class="b", nlpar="main"), ## skeptical prior with mean suggestive of antibiotics/ temp having a protective effect i.e. what we don't expect, plus a narrow sd
            prior(horseshoe(1), class="b", nlpar="reg"))


#Run model
bmod3 <- brm(formula = form,
            data=df,
            family=bernoulli(link="identity"),
            prior=priors,
            warmup = 1000, iter = 10000, thin=2, chains = 4, seed=42, cores=4, control = list(adapt_delta = 0.98))
```

```{r}
mod_df(bmod3)

```
