---
title: "main ctx_m"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

##Introduction

This document will go through the stages of univariable screening.

The variable selection method used in this document is considered to be the 'traditional veterinary epidemiology' method as is used in the majority of similar studies. Further work will be done using more modern and robust variable selection methods.




```{r include=FALSE}
rm(list = ls())
library(tidyverse)
library(readxl) 
library(visdat)
library(multcomp)
library(lme4)
library(lmerTest)
library(arm)


```

Load dataframe (available at request via NERC open access)

Perform the following cleaning:
o	Removal of zero plain counts
o	Scale and centre numerical variables
o	Selected only relevant antibiotic usage variables
o	Remove variables with too few or too many levels
o	Make the dependent variable an integer


Previous work has determined that farm should be added as a random effect.

# Variable screening

Univariable logistic regression analysis of each variable, with farm added as a random effect.

Adjust the p values to represent a false detection rate to account for the large number of variables and therefore liklihood of low ps occuring by chance.

Create a table with every variable with its OR, CI and adjusted p.

```{r include=FALSE}

 vars <- names(df)

# loop over each variable
for(i in 8:length(vars))
   
   
 {
# use trycatch so that if there is an error the loop doesn't stop
   tryTest = tryCatch(

   {
     # run the model
     uni_model <- glmer(ctx_m ~ get(vars[i])  + (1 | farm), data=df, family=binomial)
     # create model output
 p <- coef(summary(uni_model))[-1,4]
 p <- p[1]
 summary <- as.data.frame(coef(summary(uni_model)))[-1, ]
 summary <- summary[1,]
 summary <- mutate(summary, Estimate=exp(Estimate),
                   `Std. Error`=exp(`Std. Error`))%>%
   dplyr::rename(OR=Estimate,
          st.error=`Std. Error`,
          z_value=`z value`,
          p=`Pr(>|z|)`)
 rownames(summary)[1] <- vars[i]

 con <- as.data.frame(confint(uni_model, method="Wald"))[3,]%>%
   dplyr:: rename(lwr=`2.5 %`, upr=`97.5 %`)%>%
   mutate(lwr=exp(lwr), upr=exp(upr))

 summary <- cbind(summary, con)
 
# if it's the first variable, create a df, otherwise bind to the existing df

 if (i==8){
   all_uni_analysis <- summary
 } else {
   all_uni_analysis <- rbind(summary, all_uni_analysis)
 }

   },
   warning = function(w) {

     print('this is warning')
     print(w)
     return(print(vars[i]))
   },
   error = function(e) {
     print('this is error')
     print(e)
     return('return string from error')
   },
   finally = {}
 )

 print(tryTest)

 
}

```




Adjust the p values using the false detection rate method

```{r}

# #Adjusted p values- fdr
 
adjusted_p <- as.data.frame(p.adjust(all_uni_analysis$p, method = "fdr"))

# add to existing df

all_uni_analysis <- cbind(all_uni_analysis, adjusted_p)
all_uni_analysis <- dplyr::rename(all_uni_analysis, p_adjusted=`p.adjust(all_uni_analysis$p, method = "fdr")`)%>%
  mutate(var=rownames(all_uni_analysis))%>%
  dplyr::select(var, everything())

```

From all of the univariable analysis, we wish to select variables with a p<=0.25

```{r}
to_enter_model <- filter(all_uni_analysis, p_adjusted<=0.25)

print(to_enter_model$var)

```
