---
title: "pw fit model"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

# Introduction

The univariable screening has been performed in another document. In this document, we will fit the multivariable model. 

```{r include=FALSE}
rm(list = ls())
library(tidyverse)
library(readxl) 
library(visdat)
library(multcomp)
library(lme4)
library(lmerTest)
library(arm)


```


Load dataframe (available at request via NERC open access)

Perform the following cleaning:
o	Removal of zero plain counts
o	Scale and centre numerical variables
o	Selected only relevant antibiotic usage variables
o	Remove variables with too few or too many levels
o	Make the dependent variable an integer


# Multivariable models

Backwards stepwise procedure.

All of the variables enter the model. At each stage the variable with the highest p value is removed, until only those with a p<0.05 remain in the model.


```{r}

mv_1 <- glmer(ctx_m ~ s_temp + f_trough_clean + f_nsaiddiarr + f_poultry +ceph_1
+ s_cefq_dct_6m +s_fram_dct_6m  + 
                (1|farm), data=df_with_na, family = binomial)

summary(mv_1)

```

Remove ceph_1

```{r}

mv_2 <- glmer(ctx_m ~ s_temp + f_trough_clean + f_nsaiddiarr + f_poultry 
+ s_cefq_dct_6m +s_fram_dct_6m  + 
                (1|farm), data=df_with_na, family = binomial)


summary(mv_2)
```

Remove nsaiddiarr

```{r}


mv_4 <-glmer(ctx_m ~ s_temp + f_trough_clean +  f_poultry 
+ s_cefq_dct_6m +s_fram_dct_6m  + 
                (1|farm), data=df_with_na, family = binomial)
summary(mv_4)



```

Remove poultry

```{r}


mv_5 <-glmer(ctx_m ~ s_temp + f_trough_clean 
+ s_cefq_dct_6m +s_fram_dct_6m  + 
                (1|farm), data=df_with_na, family = binomial)


summary(mv_5)



```

## DIC

Check DIC for each model

```{r}


print(paste("First backwards model DIC=", extractDIC(mv_1), sep=""))
print(paste("Second backwards model DIC=", extractDIC(mv_2), sep=""))
print(paste("Third backwards model DIC=", extractDIC(mv_4), sep=""))
print(paste("Fourth backwards model DIC=", extractDIC(mv_5), sep=""))
```


Model checking will be performed in another document

