---
title: "check tet"
output:
  word_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load models- main model and skeptical prior model

```{r include=FALSE}
library(tidyverse)
library(brms)
library(bayestestR)

```

# Model checking

## Rhat

Check Rhat for all variable and for any model warnings or divergence issues.

```{r}

summary(m1)

```

## Create table for use below


Full table plus just sig variables for main model plus skeptical priors

```{r}

models=list(m1, m2)
names=c("tet_main", "tet_sk_pr")

for (i in 1:length(models)){
  fix_df <- data.frame(fixef(models[[i]]))
  fix_df$term <- row.names(fix_df)

  tmp <- effective_sample(models[[i]])%>%
    mutate(Parameter=str_remove(Parameter, "b_"))%>%
    dplyr::rename(term=Parameter, Eff.sample_size=ESS)%>%
    filter(!term=="main_intercept")

  fix_df <- left_join(fix_df, tmp, by=c("term"))
  fix_df <- fix_df %>%
    dplyr::select(term, everything(), -Est.Error) %>%
    #arrange(desc(abs(Estimate))) %>%
    filter(!grepl('Intercept', term)) %>%
    mutate_at(vars(-term, -Eff.sample_size), exp) %>%
    dplyr::rename(Variable=term, OR=Estimate, Lwr_CI=Q2.5, Upr_CI=Q97.5) %>%
    mutate(sig=if_else((Lwr_CI>1&Upr_CI>1)|(Lwr_CI<1&Upr_CI<1), 1, 0))
  sig <- filter(fix_df, sig==1)%>%
    dplyr::select(-sig)
  print(fix_df)
  print(sig)
  
  if (i==1){
    tmp_1 <- tmp
    fix_df1 <- fix_df
    sig_1 <- sig
  } else
  { 
    tmp_2 <- tmp
    fix_df2 <- fix_df
    sig_2 <- sig
    }
  
  
}

```


## Trace plots

For the important variables

```{r}
library(bayesplot)
posterior <- as.matrix(m1)
sig_1$Variable <- if_else(sig_1$Variable=="main_mes_temp0.61",
                          paste("bsp_", sig_1$Variable, sep=""),
                          paste("b_", sig_1$Variable, sep=""))
var <- sig_1$Variable

for (i in 1:length(var)){

p <- mcmc_trace(posterior,
           pars = var[i],
           facet_args = list(ncol=1, strip.position="left"))
  
print(p)
}

```

## Posterior distributions

For the important variables

```{r}



plot_title <- ggtitle("Posterior distributions with medians and 95% credible intervals")
mcmc_areas(posterior,
           pars = var,
           prob = 0.95) + plot_title


```

## Skeptical priors

Check no major change in coefficents