---
title: "Cipro pw Bayes"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

```

# Introduction

This document will go through the process of fitting a Bayesian lasso model

Load dataframe (available at request via NERC open access)

Perform the following cleaning:
o	Removal of zero plain counts
o	Scale and centre numerical variables
o	Selected only relevant antibiotic usage variables
o	Remove variables with too few or too many levels
o	Make the dependent variable an integer

# Bayesian lasso

```{r}
# Make a copy of the dataframe
df <- data.frame(df)

# Label variable categories
main_vars <- c('total_mg_pcu', 'ceph_3_4', 'fq', 'novobiocin')
re <- 'farm'
dv <- 'cipR'
all_named_vars <- c(dv, re, main_vars)

# sort variables for ease
df <- dplyr::select(df, all_named_vars, dplyr::everything())


# Make a formula
names_classes <- sapply(names(df), function(x) class(df[[x]]))
```


Reference used for the following:

Carvalho CM, Polson NG, Scott JG, The horseshoe estimator for sparse signals, Biometrika, 2010; 97:465-480

```{r}
# Make formula for horseshoe variables
horse_form <- ""
for (i in 1:length(names_classes)){
  x <- names(names_classes)[i]
  # don't add random effects, dependent variables or the main testing variables. 
  if (!x %in% c(re, dv, main_vars)){
    if ('ordered' %in% names_classes[x][[1]]){
      
      horse_form <- paste(horse_form, sprintf('%s', x), sep='+')
    }else{
      horse_form <- paste(horse_form, sprintf('%s', x), sep='+')
    }    
  }
}
horse_form <- substring(horse_form, 2)

horse_form

```

## Fit model

```{r}
library(brms)

# This follows the example https://discourse.mc-stan.org/t/horseshoe-prior-on-subset-of-predictors/8140/4
# Write a maximally explicit formula: dependent_var ~ main_vars + regularized_vars + random effect

form <- bf(cipR ~  main + reg + rand, nl=T)
form <- form + lf(rand ~ 0 + (1|farm), cmc=F, center=F)
form <- form + lf("main ~ total_mg_pcu+ceph_3_4+fq+novobiocin",cmc=F)
form <- form + lf(paste("reg ~ 0 + ",horse_form), cmc=F)
# form <- form + lf(inter ~ 1, center=T)
print

# Check which priors we need
get_prior(form, data=df, family=bernoulli)

# define the priors
priors <- c(prior(student_t(3, 0, 10), class="b", nlpar="main", coef='Intercept'),
            prior(normal(0, 5), class="b", nlpar="main"),
            prior(horseshoe(1), class="b", nlpar="reg"))

# Run model
bmod <- brm(formula = form,
            data=df,
            family=bernoulli,
            prior=priors,
            warmup = 1000, iter = 2000, chains = 4, seed=42, cores=4, control = list(adapt_delta = 0.98))

```

```{r}
library(bayestestR)

# create a dataframe of model output

mod_df <- function(mod){

# coefficients
fix_df <- data.frame(fixef(mod))
fix_df$term <- row.names(fix_df)

# Effective sample size
tmp <- effective_sample(mod)%>%
  mutate(Parameter=str_remove(Parameter, "b_"))%>%
  dplyr::rename(term=Parameter, Eff.sample_size=ESS)%>%
  filter(!term=="main_intercept")

# merge
fix_df <- right_join(fix_df, tmp, by=c("term"))

# tidy up
fix_df <- fix_df %>%
  dplyr::select(term, everything(), -Est.Error) %>%
  arrange(desc(abs(Estimate))) %>%
  filter(!grepl('Intercept', term)) %>%
  mutate_at(vars(-term, -Eff.sample_size), exp)%>%
  dplyr::rename(Variable=term, OR=Estimate, Lwr_CI=Q2.5, Upr_CI=Q97.5)%>%
  mutate(sig=if_else((Lwr_CI>1&Upr_CI>1)|(Lwr_CI<1&Upr_CI<1), 1, 0))

print(fix_df)

}

mod_df(bmod)
```

# Skeptical priors

Rerun with skeptical priors on the main variables
- we don't expect antibiotics to be protective so set this as the mean

```{r}

priors <- c(prior(student_t(3, 0, 10), class="b", nlpar="main", coef='Intercept'),
            prior(normal(-0.5, 2), class="b", nlpar="main"), ## skeptical prior with mean suggestive of antibiotics having a protective effect i.e. what we don't expect
            prior(horseshoe(1), class="b", nlpar="reg"))

# Run model
mod_2 <- brm(formula = form,
            data=df,
            family=bernoulli,
            prior=priors,
            warmup = 1000, iter = 2000, chains = 4, seed=42, cores=4, control = list(adapt_delta = 0.98))
#summary(mod_2)


```

```{r}
# create df of output as above

mod_df(mod_2)
```

