---
title: "check_model"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```


```{r include=FALSE}
rm(list = ls())

library(tidyverse)
library(kableExtra)
library(brms)
library(tidybayes)


```

# Introduction

This document will perform checks on the previously fitted model.

Load the models saved from the previous document.

# Model interpretation

Check for any warning messages or divergence issues

```{r}

summary(mod)
```

## Table of values from the model

This table shows values from the model with the variables ordered by effect size. 

```{r}

library(bayestestR)

mod_df <- function(mod){

# coefficients
fix_df <- data.frame(fixef(mod))
fix_df$term <- row.names(fix_df)

# Effective sample size
tmp <- effective_sample(mod)%>%
  mutate(Parameter=str_remove(Parameter, "b_"))%>%
  dplyr::rename(term=Parameter, Eff.sample_size=ESS)%>%
  filter(!term=="main_intercept")

# merge
fix_df <- right_join(fix_df, tmp, by=c("term"))

# tidy up
fix_df <- fix_df %>%
  dplyr::select(term, everything(), -Est.Error) %>%
  arrange(desc(abs(Estimate))) %>%
  filter(!grepl('Intercept', term)) %>%
  mutate_at(vars(-term, -Eff.sample_size), exp)%>%
  dplyr::rename(Variable=term, OR=Estimate, Lwr_CI=Q2.5, Upr_CI=Q97.5)%>%
  mutate(sig=if_else((Lwr_CI>1&Upr_CI>1)|(Lwr_CI<1&Upr_CI<1), 1, 0))

}
mod_df(mod)
```

# Diagnostics

## Convergence

Check Rhat and examine trace plots below.

## Trace and density plots

For the important variables

```{r}
plot(mod, pars=c("main_fq", "reg_s_percentdryoff"), combo = c("dens","trace"))
#summary(mod)


library(bayesplot)

posterior <- as.matrix(mod)

plot_title <- ggtitle("Posterior distributions",
                      "with medians and 95% intervals")
mcmc_areas(posterior,
           pars = c("b_main_fq", "b_reg_s_percentdryoff"),
           prob = 0.95) + plot_title

```


## Marginal effects

Plot the marginal effects of the two most important variables.


```{r}
marginal_effects(mod, effects=c("fq",
                                "s_percentdryoff"), par=FALSE)

```


## Skeptical priors

Read in model fitted in previous document and check for any changes in coefficients.