---
title: "end point for paper"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
rm(list = ls())
library(tidyverse)
library(visdat)
library(readxl)

```

Load data
Scale numerical variables

# Introduction

This document will go through the process of fitting the individual heifer sample models.

# Functions

```{r include=FALSE}
# function to create df of model output

mod_output <- function(mod){

m <- as.data.frame(coef(summary(mod)))
m <- m%>%  mutate(var=rownames(m))
m <-m%>%  mutate(Estimate=exp(Estimate))%>%
  dplyr::rename(OR=Estimate,
                p=`Pr(>|z|)`)

con <- as.data.frame(confint(mod, method="Wald"))[-1,]%>%
   dplyr:: rename(lwr=`2.5 %`, upr=`97.5 %`)%>%
   mutate(lwr=exp(lwr), upr=exp(upr))

 summary <- cbind(m, con)%>%
   dplyr::select(var, OR, lwr, upr, p)%>%
   mutate(p=round(p, digits=4))%>%
   arrange(p)%>%
   filter(!var=="(Intercept)")
 
 print(summary)
}


```


# Analysis

Three anlyses will be performed.
1. Examining the environmental samples over the whole project period
2. Examining the environmental samples during the last three months
3. Examining the environmental samples over the whole period for heifers only

Zero plain counts are excluded from the environmental samples before averaging.

Variable selection: performed using prior knowledge and based on the original OH STAR hypothesis.
Dependent variable= binary resistance
Random effects= farm
Fixed effects= 
* proportion of environmental samples taken from that farm with the type of resistance being tested
* rectal or cowpat
* run by EW or KM
* AMU variables from each farm to include total AMU and antibiotics relevent to the resistance being tested

All variables will be included in the initial model; then a backwards stepwise approach will be taken where the variable with the highest p value is removed on each iteration until only those with p < 0.05 remain.

## Amoxicillin

### All environmental samples

Multivariable logistic regression with variables as described above.

```{r}

library(lme4)

mod1 <- glmer(amoxR ~ farm_amoxR_pc_ex + code+ run_by + temp_farm+ total_mg_pcu+amox+co_amox+pen+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ farm_amoxR_pc_ex + code+ run_by + temp_farm+ total_mg_pcu+co_amox+pen+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ farm_amoxR_pc_ex + code+ run_by + temp_farm+ co_amox+pen+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ farm_amoxR_pc_ex + code+ run_by + temp_farm+ pen+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ farm_amoxR_pc_ex + code+ run_by + temp_farm+ (1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ farm_amoxR_pc_ex + code+ run_by +(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ code+ run_by +(1|farm), data=df, family=binomial)

mod_output(mod1)

```


### Last 3m environmental samples

Multivariable logistic regression with variables as described above.

```{r}

mod1 <- glmer(amoxR ~ farm_amoxR_pc_ex_3m + code+ run_by + temp_3m+ total_mg_pcu+amox+co_amox+pen+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ farm_amoxR_pc_ex_3m + code+ run_by + temp_3m+ total_mg_pcu+amox+co_amox+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ farm_amoxR_pc_ex_3m + code+ run_by + temp_3m+ amox+co_amox+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ farm_amoxR_pc_ex_3m + code+ run_by + temp_3m+ co_amox+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ farm_amoxR_pc_ex_3m + code+ run_by + temp_3m+ (1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ farm_amoxR_pc_ex_3m + code+ run_by +(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~  code+ run_by +(1|farm), data=df, family=binomial)

mod_output(mod1)

```

### Just heifers (NB last three months wouldn't be enough samples)

```{r}
mod1 <- glmer(amoxR ~ heif_amoxR_pc_ex + code+ run_by + temp_heif+ total_mg_pcu+amox+co_amox+pen+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ heif_amoxR_pc_ex + code+ run_by + temp_heif+ total_mg_pcu+co_amox+pen+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ heif_amoxR_pc_ex + code + run_by +temp_heif+co_amox+pen+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ heif_amoxR_pc_ex + code + run_by +temp_heif+pen+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ heif_amoxR_pc_ex + code + run_by +pen+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~ heif_amoxR_pc_ex + code + run_by +(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(amoxR ~  code + run_by +(1|farm), data=df, family=binomial)

mod_output(mod1)


```

## Tetracycline

### All environmental samples

Multivariable logistic regression with variables as described above.

```{r}

mod1 <- glmer(tetR ~ farm_tetR_pc_ex + code+ run_by + temp_farm+ total_mg_pcu+tet+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(tetR ~ code+ run_by + temp_farm+ total_mg_pcu+tet+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(tetR ~ code+ run_by + temp_farm+ total_mg_pcu+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(tetR ~ code+ run_by +  total_mg_pcu+(1|farm), data=df, family=binomial)

mod_output(mod1)

```

### Last 3m environmental samples

Multivariable logistic regression with variables as described above.

```{r}

mod1 <- glmer(tetR ~ farm_tetR_pc_ex_3m + code+ run_by + temp_3m+ total_mg_pcu+tet+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(tetR ~ farm_tetR_pc_ex_3m + code+ run_by + temp_3m+ tet+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(tetR ~ farm_tetR_pc_ex_3m + code+ run_by + temp_3m+ (1|farm), data=df, family=binomial)

mod_output(mod1)
 
```

### Just heifers


```{r}

mod1 <- glmer(tetR ~ heif_tetR_pc_ex + code+ run_by + temp_heif+ total_mg_pcu+tet+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(tetR ~  code+ run_by + temp_heif+ total_mg_pcu+tet+(1|farm), data=df, family=binomial)

mod_output(mod1)

mod1 <- glmer(tetR ~  code+ run_by +  total_mg_pcu+tet+(1|farm), data=df, family=binomial)

mod_output(mod1)
 
mod1 <- glmer(tetR ~  code+ run_by +  total_mg_pcu+(1|farm), data=df, family=binomial)

mod_output(mod1)
 
```

## Cefalexin

### All environmental samples

```{r}
mod3 <- glmer(cephR ~ farm_cephR_pc_ex + code+ run_by + temp_farm+ total_mg_pcu+ceph_1+ceph_3_4+cefalexin+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ farm_cephR_pc_ex + code+ run_by + temp_farm+ ceph_1+ceph_3_4+cefalexin+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ farm_cephR_pc_ex + code+ run_by + temp_farm+ ceph_1+ceph_3_4+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ farm_cephR_pc_ex + code+ temp_farm+ ceph_1+ceph_3_4+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ farm_cephR_pc_ex + code+  ceph_1+ceph_3_4+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ code+  ceph_1+ceph_3_4+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ code+  ceph_1+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ code+  (1|farm), data=df, family=binomial)

mod_output(mod3)

```
 
### Last 3m environmental samples

```{r}
mod3 <- glmer(cephR ~ farm_cephR_pc_ex_3m + code+ run_by + temp_3m+ total_mg_pcu+ceph_1+ceph_3_4+cefalexin+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ farm_cephR_pc_ex_3m + code+  temp_3m+ total_mg_pcu+ceph_1+ceph_3_4+cefalexin+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ farm_cephR_pc_ex_3m + code+  temp_3m+ ceph_1+ceph_3_4+cefalexin+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ farm_cephR_pc_ex_3m + code+  temp_3m+ ceph_1+cefalexin+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ farm_cephR_pc_ex_3m + code+  temp_3m+ cefalexin+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ farm_cephR_pc_ex_3m + code+  temp_3m+ (1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~  code+  temp_3m+ (1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~  code+  (1|farm), data=df, family=binomial)

mod_output(mod3)

```

### Just heifers

```{r}
mod3 <- glmer(cephR ~ heif_cephR_pc_ex + code+ run_by + temp_heif+ total_mg_pcu+ceph_1+ceph_3_4+cefalexin+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ heif_cephR_pc_ex + code+ run_by + temp_heif+ ceph_1+ceph_3_4+cefalexin+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ heif_cephR_pc_ex + code+ run_by +  ceph_1+ceph_3_4+cefalexin+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ heif_cephR_pc_ex + code+ run_by +  ceph_1+ceph_3_4+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ heif_cephR_pc_ex + code+  ceph_1+ceph_3_4+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ code+  ceph_1+ceph_3_4+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ code+  ceph_1+(1|farm), data=df, family=binomial)

mod_output(mod3)

mod3 <- glmer(cephR ~ code+  (1|farm), data=df, family=binomial)

mod_output(mod3)
```
