---
title: "check endpoint models"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
rm(list = ls())
library(tidyverse)
library(visdat)
library(readxl)

```

Load main data
Scale numerical variables
Read in models fitted in previous document

# Introduction

This document will perform checks on the individual heifer models.


# Functions

## Model output

```{r include=FALSE}
# function to create df of model output

mod_output <- function(mod){

m <- as.data.frame(coef(summary(mod)))
m <- m%>%  mutate(var=rownames(m))
m <-m%>%  mutate(Estimate=exp(Estimate))%>%
  dplyr::rename(OR=Estimate,
                p=`Pr(>|z|)`)

con <- as.data.frame(confint(mod, method="Wald"))[-1,]%>%
   dplyr:: rename(lwr=`2.5 %`, upr=`97.5 %`)%>%
   mutate(lwr=exp(lwr), upr=exp(upr))

 summary <- cbind(m, con)%>%
   dplyr::select(var, OR, lwr, upr, p)%>%
   mutate(p=round(p, digits=4))%>%
   arrange(p)%>%
   filter(!var=="(Intercept)")
 

}


```

## AUC

```{r}
# create auc function

auc_roc <- function(mod){
  # calculates auc for a model ('mod') given the observations in the data
  
  # make predictions
  predp <- predict(mod, type=c("response"))
  
  # get the actual responses in the data
  roc_obj<- pROC::roc(slot(mod, 'resp')$y ~ predp)
  
  # calculate auc
  pROC::auc(roc_obj)
  }


```

# Summary for each model

```{r}
models= list(amox_farm, amox_farm_3m, amox_heif, tet_farm, tet_farm_3m, tet_heif, ceph_farm, ceph_farm_3m, ceph_heif)

for (i in 1:length(models)){
  
  print(summary(models[[i]]))
}


```

Note: all amox and ceph final models are the same.
Tet farm and heifers both the same. 3 month model is different.

```{r}
amox_all <- amox_farm
ceph_all <- ceph_farm
tet_3m <- tet_farm_3m
tet_12m <- tet_farm


```


# Output and AUC for each model

```{r}
models= list(amox_all, tet_12m, tet_3m, ceph_all)

labels= list("amox_all", "tet_12m", "tet_3m", "ceph_all")

for(i in 1:length(models)){

m = mod_output(models[[i]])
m = mutate(m, model=labels[[i]], auc=(auc_roc(models[[i]])))
  
if (i==1) {
  all_mod <- m
}  else {
  all_mod <- rbind(all_mod, m)
}
  print(summary(models[[i]]))

}


```

# Multicollinearity

We will run each variable in turn and check for no 'significant' change in the resulting coefficients, based on whether the coefficients remain within the error bars of the other models.

## Amoxicillin

```{r}
library(arm)

# run each model
mv_1 <-glmer(amoxR ~ code+(1|farm), data=df, family=binomial)

mv_2 <- glmer(amoxR ~ run_by +(1|farm), data=df, family=binomial)

mv_3 <- glmer(amoxR ~ code+run_by +(1|farm), data=df, family=binomial)


models= list(mv_1, mv_2, mv_3)

# create df of all mod output

for (i in 1:length(models)) {
 
    
    mv <-  mod_output(models[[i]])%>%
      mutate(model=paste("mv", i, sep=""))
     
      if  (i==1)
      { mv_all <- mv
     
          } else {
                    mv_all <- rbind(mv, mv_all)
          }
     }
  
 
# graph of coefficients for each model spec and error bars
 mv <- mv_all
p <- ggplot(data=mv, aes(x=model, y=OR, group=var)) +
  geom_line(aes(color=var), size=2)+
  geom_point()+
  geom_errorbar(aes(ymin=lwr, ymax=upr), width=.2,
                 position=position_dodge(0.05))
  #geom_vline(xintercept = 4, color="yellow", width=1.5)

p 

```

## Tetracycline 3m


```{r}
library(arm)
mv_1 <-glmer(tetR ~ run_by+temp_3m+farm_tetR_pc_ex_3m+(1|farm), data=df, family=binomial)

mv_2 <- glmer(tetR ~ code+temp_3m+farm_tetR_pc_ex_3m+(1|farm), data=df, family=binomial)

mv_3 <- glmer(tetR ~ code+run_by+farm_tetR_pc_ex_3m+(1|farm), data=df, family=binomial)

mv_4 <- glmer(tetR ~ code+run_by+temp_3m+(1|farm), data=df, family=binomial)

models= list(mv_1, mv_2, mv_3, mv_4)

for (i in 1:length(models)) {
 
    
    mv <-  mod_output(models[[i]])%>%
      mutate(model=paste("mv", i, sep=""))
     
      if  (i==1)
      { mv_all <- mv
     
          } else {
                    mv_all <- rbind(mv, mv_all)
          }
     }
  
 
 mv <- mv_all
p <- ggplot(data=mv, aes(x=model, y=OR, group=var)) +
  geom_line(aes(color=var), size=2)+
  geom_point()+
  geom_errorbar(aes(ymin=lwr, ymax=upr), width=.2,
                 position=position_dodge(0.05))
  #geom_vline(xintercept = 4, color="yellow", width=1.5)

p 

```

## Tetracycline all
```{r}
library(arm)
mv_1 <-glmer(tetR ~ code+total_mg_pcu+(1|farm), data=df, family=binomial)

mv_2 <- glmer(tetR ~ run_by+total_mg_pcu+(1|farm), data=df, family=binomial)

mv_3 <- glmer(tetR ~ run_by+code+(1|farm), data=df, family=binomial)

models= list(mv_1, mv_2, mv_3)

for (i in 1:length(models)) {
 
    
    mv <-  mod_output(models[[i]])%>%
      mutate(model=paste("mv", i, sep=""))
     
      if  (i==1)
      { mv_all <- mv
     
          } else {
                    mv_all <- rbind(mv, mv_all)
          }
     }
  
 
 mv <- mv_all
p <- ggplot(data=mv, aes(x=model, y=OR, group=var)) +
  geom_line(aes(color=var), size=2)+
  geom_point()+
  geom_errorbar(aes(ymin=lwr, ymax=upr), width=.2,
                 position=position_dodge(0.05))
  #geom_vline(xintercept = 4, color="yellow", width=1.5)

p 

```

