---
title: "ampc fit model"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


The univariable screening has been performed in another document. In this document, we will fit the multivariable model. 

```{r include=FALSE}
rm(list = ls())
library(tidyverse)
library(readxl) 
library(visdat)
library(multcomp)
library(lme4)
library(lmerTest)
library(arm)


```

Load dataframe (available at request via NERC open access)

Perform the following cleaning:
o	Removal of zero plain counts
o	Scale and centre numerical variables
o	Selected only relevant variables
o	Remove variables with too few or too many levels
o	Make the dependent variable an integer


# Multivariable models

Backwards stepwise procedure.

All of the variables identified from the univariable analysis as important enter the model. At each stage the variable with the highest p value is removed, until only those with a p<0.05 remain in the model.


```{r}
 mv_1 <- glmer(amp_c ~ co_amox+ total_mg_pcu+ s_housed_outdoor+f_pattern+  footpath+preweaned_heifer+adult+weaned_heifer+f_pneum_vacc+(1|farm), data=df, family=binomial)

summary(mv_1)

```

Remove footpath
```{r}
 mv_2 <- glmer(amp_c ~ co_amox+ total_mg_pcu+ s_housed_outdoor+f_pattern+  preweaned_heifer+adult+weaned_heifer+f_pneum_vacc+(1|farm), data=df, family=binomial)

summary(mv_2)



```

Remove weaned heifer

```{r}
 mv_3 <- glmer(amp_c ~ co_amox+ total_mg_pcu+ s_housed_outdoor+f_pattern+  preweaned_heifer+adult+f_pneum_vacc+(1|farm), data=df, family=binomial)
summary(mv_3)



```

Remove adult

```{r}
 mv_4 <- glmer(amp_c ~ co_amox+ total_mg_pcu+ s_housed_outdoor+f_pattern+  preweaned_heifer+
                 f_pneum_vacc+(1|farm), data=df, family=binomial)


summary(mv_4)


```

Remove total amu

```{r}
 mv_5 <- glmer(amp_c ~ co_amox+ s_housed_outdoor+f_pattern+  preweaned_heifer+
                 f_pneum_vacc+(1|farm), data=df, family=binomial)

summary(mv_5)

#forage_type_3 = maize

```


# DIC
Look at DIC for first and last model

```{r}
print(paste("First backwards model DIC=", extractDIC(mv_1), sep=""))
print(paste("Final backwards model DIC=", extractDIC(mv_5), sep=""))

```

# Table of key values from final model

```{r}


mv <- as.data.frame(coef(summary(mv_5)))[-1,]
  
      mv <- mutate(mv, var=rownames(mv),
                 #auc=auc_roc(mv_5), 
                 dic=extractDIC(mv_5))%>%
      dplyr::rename(OR=Estimate, p=`Pr(>|z|)`, se=`Std. Error`, z_value=`z value`)%>%
        mutate(z_value=NULL, lwr=OR-2*se, upr=OR+2*se)%>%
        mutate_at(vars(OR, lwr, upr, se), exp)%>%
        dplyr::select(var, everything())

print(mv)

```

Model checking to be done in a different document.